---
title: "WHO - Life Expectancy"
author: 'Author: Daniel Syahputra'
date: 'Las Updated: `r Sys.Date()`'
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    df_print: paged
    theme: united
    highlight: zenburn
    css: assets/style.css
    mathjax: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction {.tabset}

### Abstract

### About data

The dataset related to life expectancy, health factors for 193 countries has been collected from WHO data repository website. This dataset contains 2938 rows with 22 features / columns which can be accessed on [Kaggle](https://www.kaggle.com/kumarajarshi/life-expectancy-who). Let see description for each attribute in this dataset:

-   `Country`:

-   `Year`

-   `Status`

-   `Life.expectancy`

-   `Adult.Mortality`

-   `infant.deaths`

-   `Alcohol`

-   `percentage.expenditure`

-   `Hepatitis.B`

-   `Measles`

-   `BMI`

-   `under.five.deaths`

-   `Polio`

-   `Total.expenditure`

-   `Diphtheria`

-   `HIV.AIDS`

-   `GDP`

-   `Population`

-   `thinness..1.19.years`

-   `thinness.5.9.years`

-   `Income.composition.of.resources`

-   `Schooling`

As we see from those attribute above, there some attributes with not clear name. So, in data preparation we'll rename some columns.

### Goals

## Data Preparation

```{r}
life_expectancy <- read.csv("datasets/life_expectancy.csv")
unique(life_expectancy$Year)
```
